% Modes: draft/proof/final % Optional: debug, online
\documentclass[online,masters,deptscs,forcegraphics,final]{ruthesis}

\usepackage[backend=biber,bibencoding=utf8,style=ieee]{biblatex}
\addbibresource{references.bib}

\usepackage{custom}

\newML{program}{Computer Science}{Tölvunarfræði}
\program{\MLprogram}

% Supervisor's signature (\MLjan, \MLfeb, \MLmar, ... \MLdec)
\whensigned{10}{\MLmay}{2021}

\newML{Title}{Automated bijections with combinatorial exploration}{Sjálfvirknivæddar gagntækar varpanir með fléttufræðilegri könnun}
\newML{TITLE}{AUTOMATED BIJECTIONS WITH COMBINTAORIAL EXPLORATION}{SJÁLFVIRKNIVÆDDAR GAGNTÆKAR VARPARNI MEÐ FLÉTTUFRÆÐILEGRI KÖNNUN}
\setTitle{\MLTitle}{\MLTITLE}

\author{J\'{o}n~Steinn~El\'{i}asson}

\ects{30}

% \MLSeniorProfessor \MLProfessor \MLAssociateProfessor \MLAdjunctProfessor \MLEmeritusProfessor \Iceland \MLReykjavikUniversity \MLUniversityIceland
\supervisors{
  \personinfo{Henning Ulfarsson}{\MLSupervisor}{Assistant Professor}{\MLReykjavikUniversity}{\MLIceland}
  \personinfo{Christian Bean}{Co-advisor}{Postdoctoral Researcher}{\MLReykjavikUniversity}{\MLIceland}
}
\examiners{
  \personinfo{Jay Pantone}{\MLExaminer}{Assistant Professor}{Marquette University}{United States}
  \personinfo{Émile Nadeau}{\MLExaminer}{Doctoral Student}{\MLReykjavikUniversity}{\MLIceland}
}


\newML{AbstractText}{\input{chapters/00_A_en_abstract}}{\input{chapters/00_B_is_abstract}}
\setAbstract{\MLAbstractText}

\makeindex{}
\indexintoc{}

\finalifforcegraphics{hyperref}
\usepackage[hidelinks]{hyperref} 


%\usepackage{lineno}
%\linenumbers
\definecolor{todocolor}{RGB}{205,235,139}
\definecolor{todo-idea}{RGB}{120,180,255}
\definecolor{todo-error}{RGB}{208,31,60}
\definecolor{todo-question}{RGB}{255,255,136}
\usepackage[colorinlistoftodos, color=todocolor, textsize=small]{todonotes}

\input{macros}

\begin{document}
\frontmatter{}

\frontrequiredpages{}


%% Dedication is optional, comment out if it is absent
%% RUM: Not mentioned
\begin{dedications}
I dedicate this thesis to my wife, Sólborg Erla Ingvarsdóttir, and our sons,\\ Ingvar Sölvi Jónsson and Þorkell Ari Jónsson.
\end{dedications}

\enableindents{}

\coverchapter{Acknowledgements} 
Acknowledgement text...

\starttables{}% setup formatting

\tableofcontents{}\clearpage%%RUM: "Table of contents"
\listoffigures{}\clearpage%%RUM: "List of figures"
\listoftables{}\clearpage%%RUM: "List of tables"
\listoffixmes{}

\starttext{}

\todo[inline,caption={}]{JSE: General notes
\begin{itemize}
    \item Use ``respectively'' less
    \item Find pages in books for references
    \item Prune backgr of info that I don't end up using (will probably use everything though)
    \item Constructors can be unary (e.g. seq), update to stop conditioning on out-degree (this should be updated in code too if it is done there)
    \item Example of non-admissible constructors? Do we use any such constr.? Should we?
    \item Resize graph nodes for $\set{x}$ to be same as others.
    \item Rethink equiv when introducing fusion
    \item discuss meaning of defs prior to (not after) them?
    \item consistency with equivalence equivalent
    \item List of Algorithms? Listings?
    \item ProofTrees are noted as grammar in figs (intentionally vague), define if I want to use the word prooftrees
    \item If we get this to work for fusion and it doesn't fit into this, add a ch/sec for it and touch on differences.
    \item Simplify everything once we have connected ch 3 and 4, especially those cases functions
    \item Use unique greek letters (etc) for different things. Especially phi and varphi (which I usually overuse). Make a list of everything used (and for what purpose) to get an overview. Then assign unique symbols. Leave some symbols for 'let symb be a'
    \item comma+period in functions w cases
    \item use eq-environments more, that is... reduce `complicated` stuff flowing in text
    \item some figures probably need subfigures (a), (b), ...
\end{itemize}
}
\clearpage

\input{chapters/01_introduction}\clearpage
\input{chapters/02_background}\clearpage
\input{chapters/03_parallel}\clearpage
\input{chapters/04_bijections}\clearpage
\input{chapters/05_bijection_search}\clearpage
\input{chapters/06_results}\clearpage
\input{chapters/07_cremark}\clearpage

\printbibliography{}

\begin{appendices}
\input{chapters/A_min_example}\clearpage
\input{chapters/B_symbols}\clearpage
\end{appendices}

\clearforchapter{}

\end{document}