\coverchapter{Introduction}\label{ch:introduction}
The name combinatorics is derived from the word combinations. It is the field of mathematics concerned with the study of discrete structures. One of its most prominent subfields is enumerative combinatorics. How many unique finite structures of a specific type and size exist? This is the fundamental question of enumerative combinatorics. Two of the most important tools in the enumerative combinatorialist's toolkit are generating functions and bijections.

Permutations are an example of a finite structure. A permutation pattern is subsequence obeying certain conditions. The study of permutation patterns can be traced to \authcite{MacMahon} where he enumerated permutations that can be divided into two decreasing subsequences. In contemporary notation, he was describing the avoidance of the pattern $123$. The permutations sortable by a stack were shown to be those avoiding the pattern $231$ in \authcite{knuth:aocp1}. That was the catalyst for the surge of interest in the study of permutation patterns. A second catalyst was the first bijections between pattern avoiding permutations in \authcite{simionandschmidt}. 

The first automated enumeration was done by \authcite{Zeilberger1998EnumerationSA} which was later extended by \authcite{vatter_2008}. A more recent approach, Combinatorial Exploration, was introduced by \authcite{BeanPhd:phd}. It is a domain independent automated enumeration framework. Its implementation is called \href{https://github.com/PermutaTriangle/comb_spec_searcher}{\texttt{CombSpecSearcher}} and has since been developed further. Given a programmatical interpretation of a finite structure it will attempt to find a structural description which can be translated to a set of equations whose solution is the structure's generating function.

The translation method described by \authcite{wood_zeilberger} is an automated way of constructing bijections. In order to apply, it requires an algebraic proof so in a sense, it is not fully automated. A fully automated process of finding and constructing bijections does not exist as far as we know.

Our aim is to incorporate the other essential enumerative combinatorialist's tool, bijections, into Combinatorial Exploration. We implement a bijection based on the structural description output by the framework and furthermore, a search method for bijections in the expanded universe that Combinatorial Exploration uses in its search. We provide a domain independent fully automated method to find and construct bijections. This paper will describe the algorithms used (which have all been implemented in Python) and construct the theoretical foundation needed. As a proof of concept we connect numerous sets with bijections, mainly focusing on sets of permutations.

This thesis is structured as follows. \ChapterRef{ch:backgr} will cover prerequisites. In \ChapterRef{ch:parallel} we define criteria that must hold so a bijection can be constructed and in \ChapterRef{ch:pbijection} we define the resulting bijection. The search method for bijections is described in \ChapterRef{ch:search}. We state notable successes in \ChapterRef{ch:results} and reflect on our work in \ChapterRef{ch:conclusion}.
